Predicting sales of newly published books

### 2015-08-24 paper.tex
contestando comentarios de Pablo

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem or predicting sales to %FERGU: The problem ON predicting, no?
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
In this paper, which works with data on published books for several years in
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

%********************************************************************************
\section{Sales forecasting. State of the art} %FERGU: State of the art on sales forecasting?
\label{sec:soa}

@@

Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems, %FERGU: terminar esta frase con punto en vez de coma para que no sea larga
the efficiency of these techniques depends largely on the field of application 
and the problem data as they require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

@@

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose \cite{Moon2010ICSSSM,Moon2010ICEC} analyzing 
relationships between on-line information and book sales.
Specifically, authors propose using the number of blog references as an indicator 
of book sales.
Different sales patterns are observed by analyzing data obtained.
In any case, in this research, historical data from published books is used, %FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso
and the proposed methodology can not be usable in the problem of unpublished-books 
sales prediction.

@@

Some authors have faced the problem of forecasting sales of new products using 
different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
decision trees for sales forecasting in textile-appared fashion industry, %FERGU: appared? apparel, creo
a very similar issue to the new book publishing problem.
The same problem was previously faced by Xia et al \cite{Xia2012} using a 
forecasting method based on extreme learning machine with adaptive metrics of inputs.
Complexity of this problem is due to the lack of historical data, short lifetime 
of the large number of items, and due to the influence of variables such as 
promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems 
involving new tea, cosmetic, and soft drink products taking into account 
quantitative variables. 
In this study, it is assumed that products are classified based on their sales 
pattern so that products in the same class would have similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? 
However, as the authors state, proposed system can not deal with qualitative 
date related to the products, and even more real-world cases, such as consumer 
electronics and fashion products, should be examined, as these industries 
introduce new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
Proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method? 
online reviews and historical data.

@@

In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available. %FERGU: data es plural. is->are
In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.

@@

Trevenque company, whose expert manager advised this research, provided %FERGU: los párrafos anteriores son un poco dispersos, puedes quitar los puntos y aparte y agruparlos por temas (por ejemplo, todo lo de Trevenque debería de ir en un párrafo)
the initial data set consisting of 3159 books.
In this data set, descriptive information for each book includes price, 
selling points, matter, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

\begin{minipage}{2.3in} \begin{verbatim}
REFERENCE
AUTHOR
RETAIL PRICE
MATTER1
MATTER2
MATTER3
EDITORIAL
COLLECTION
BOOKBINDING
PRINT-RUN
TOTAL SALES
MALLS SALES
DELEGATES SALES
REST OF SALES
TOTAL SALES FIRST YEAR
MALL SALES FIRST YEAR
DELEGATES SALES FIRST YEAR
REST OF SALES FIRST YEAR
TOTAL DISTRIBUTED
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED
REST OF DISTRIBUTED
TOTAL DISTRIBUTED FIRST YEAR
MALLS DISTRIBUTED FIRST YEAR
DELEGATES DISTRIBUTED FIRST YEAR
\end{verbatim} \end{minipage}     &

@@

In this prediction problem, several variables related to the own book affect 
the forecasts, such as author, price, matter or publisher.

@@

Thus, in this study there are three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
for details): 
\begin{itemize}

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} %FERGU: mejor tratar esto como una referencia, ya que es un texto
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.

Specifically, in order to compute the forecasting errors of the different methods, %FERGU: quitar este salto de linea y unirlo al párrafo de arriba
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

\hline
\end{tabular}
\end{center}
\end{table}
%FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
variables to be considered, and taking into account the knowledge of the company 
experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analysis of dataset using the total 
of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after 
the second analysis.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, %FERGU: la figura está en español, pero ya lo sabréis :P
using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. 
        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{MATTER} were included, while %FERGU: vale, no useis MATTER, usad mejor SUBJECT (MATTER es materia de física, creo xD)
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS ON SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.

@@

\begin{minipage}{2.3in} \begin{verbatim}
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
TOTAL DISTRIBUTED
RETAIL PRICE
MATTER
EDITORIAL
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book can be shown 
in Table \ref{tabla:results7}.
Although in this dataset each book is described using a smaller number of 
variables, two categorical variables, \emph{EDITORIAL} and \emph{MATTER}, are 
included, what that makes harder to process the instances and build the different 
models.

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7} %FERGU: es normal que con menos variables tarde más?
\end{table*}

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:results13} 
and \ref{tabla:results7}, using those categorical variables as part of a big 
data set makes the problem hard to solve, both in required time to build the 
forecasting models as well as in the obtained errors.
However, as stated before, Trevenque expert sales manager, taking into account 
his knowledge in industry experience and their perceptions, decided that 
\emph{EDITORIAL} and \emph{MATTER} should be taken into account.

@@

Taking into account the SVM model obtained results, this method obtains the best %FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
errors. Even when used using the default parameter values it exhibit a good 
generalization performance.
However, it is much slower than the others to build the model, not only when 
using the data set with 13 input variables, but when using the data set with %FERGU: a veces pones dataset: unificarlo
7 input variables (including \emph{EDITORIAL} and \emph{MATTER}).

@@

As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
building (not only parameter and weights setting, but also time to train the 
network) and the fact that it is a back-box model, and thus, it is difficult 
to explain how the forecasts are obtained.
In these experiments, the MLP requires a higher time than other methods, but also
the obtained errors are worse as no parameter tuning to build the models have
been carried out.
Also, the difficulty to process information related to variables \emph{EDITORIAL} 
and \emph{MATTER} might affect the worse results obtained on the final dataset.

>>>>

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem on predicting sales to %FERGU: The problem ON predicting, no? ¡gracias!
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
In this paper, which works with data on published books for several years in
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

%********************************************************************************
\section{State of the art on sales forecasting} %FERGU: State of the art on sales forecasting?  ok  ;)
\label{sec:soa}

@@

Specifically, using time series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems. 
%FERGU: terminar esta frase con punto en vez de coma para que no sea larga.   OK
The efficiency of these techniques depends largely on the field of application 
and the problem data as they require a large amount of data for predicting 
sales of new products are not the most suitable for this task \cite{ChingChin2010}.

@@

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works propose analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}.
Specifically, authors propose using the number of blog references as an indicator 
of book sales.
Different sales patterns are observed by analyzing data obtained.
In any case, Moon et al \cite{Moon2010ICSSSM,Moon2010ICEC} used historical data from published books, 
%FERGU: a qué research se refiere? A la nuestra o a la de la referencia? Dejarlo más claro, por si acaso.   ok
and the proposed methodology can not be usable in the problem of unpublished-books 
sales prediction.

@@

Some authors have faced the problem of forecasting sales of new products using 
different data mining methods \cite{Hammond1990,Chang2009,ChingChin2010,Thomassey2012,Xia2012}. 
Thomassey et al \cite{SThomassey2014} propose using a clustering method and 
decision trees for sales forecasting in textile-apparel fashion industry, %FERGU: appared? apparel, creo.  ¡sí!
a very similar issue to the new book publishing problem.
The same problem was previously faced by Xia et al \cite{Xia2012} using a 
forecasting method based on extreme learning machine with adaptive metrics of inputs.
Complexity of this problem is due to the lack of historical data, short lifetime 
of the large number of items, and due to the influence of variables such as 
promotions, fashions, or economic environment \cite{Thomassey2012,Xia2012,SThomassey2014}.

  %[Pedro] otro caso muy similar es el paper de ChingChin2010 sobre:
  % New tea product
  % New cosmetic product
  % New soft drink product
In \cite{ChingChin2010}, a decision-support system for new product sales %FERGU: The work of Chinchin et al.?
forecasting is proposed to solve three real-world sales forecasting problems 
involving new tea, cosmetic, and soft drink products taking into account 
quantitative variables. 
In this study, it is assumed that products are classified based on their sales 
pattern so that products in the same class would have a similar sales pattern. %FERGU: "_a_ similar sales pattern", mejor? ok
However, as the authors state, proposed system can not deal with qualitative 
date related to the products, and even more real-world cases, such as consumer 
electronics and fashion products, should be examined, as these industries 
introduce new products every season.

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
The proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method?    ok
online reviews and historical data.

@@

In the case of already published books, available historical data might help 
to generate predictive models.
However, in the case of new books there is no historical data to define patterns, 
and only some descriptive data about the new book is available. 
%FERGU: data es plural. is->are   ...a mí me suena bien con "is"   ¡una segunda opinión!   ;)
In these cases not any forecasting method can be used \cite{Madsen2008,ChernWSF15}.

@@

Trevenque company, whose expert manager advised this research, provided %FERGU: los párrafos anteriores son un poco dispersos, puedes quitar los puntos y aparte y agruparlos por temas (por ejemplo, todo lo de Trevenque debería de ir en un párrafo)
the initial data set consisting of 3159 books.
In this data set, descriptive information for each book includes price, 
selling points, subject, publisher, sales, returns, among other information.
Table \ref{tabla:paramsOrig50} shows the original set of parameters describing 
each book.

@@

\begin{minipage}{2.3in} \begin{verbatim}
REFERENCE
AUTHOR
RETAIL PRICE
SUBJECT1
SUBJECT2
SUBJECT3
EDITORIAL
COLLECTION
BOOKBINDING
PRINT-RUN
TOTAL SALES
MALLS SALES
DELEGATES SALES
REST OF SALES
TOTAL SALES FIRST YEAR
MALL SALES FIRST YEAR
DELEGATES SALES FIRST YEAR
REST OF SALES FIRST YEAR
TOTAL DISTRIBUTED
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED
REST OF DISTRIBUTED
TOTAL DISTRIBUTED FIRST YEAR
MALLS DISTRIBUTED FIRST YEAR
DELEGATES DISTRIBUTED FIRST YEAR
\end{verbatim} \end{minipage}     &

@@

In this prediction problem, several variables related to the own book affect 
the forecasts, such as author, price, subject or publisher.

@@

Thus, in this study we propose three main stages (see Figure \ref{fig:stages} %FERGU: there are->we propose
for details): 
\begin{itemize}

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} %FERGU: mejor tratar esto como una referencia, ya que es un texto
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
Specifically, in order to compute the forecasting errors of the different methods, 
%FERGU: quitar este salto de linea y unirlo al párrafo de arriba.    ok
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

\hline
\end{tabular}
\end{center}
\end{table}
%FERGU: para ahorrar espacio se puede hacer la tabla inversa: variables que se han quitado (las 7)
%[pedro] no entiendo muy bien a qué te refieres...

Then, after analyzing the original dataset using the SOM to select the best %FERGU: parametros o framework SOM usados?
variables to be considered, and taking into account the knowledge of the company 
experienced manager, 13 inputs were considered. 
Figure \ref{fig:som43} shows the initial analysis of dataset using the total 
of 43 descriptive inputs per book.
Table \ref{tabla:params13} shows the set of variables describing a book after 
the second analysis.
	% esta gráfica no aporta nada, ni la siguiente tampoco. No se puede
	% colocar en un trabajo en revista  cómo ha ido el entrenamiento, sino
	% datos serios de análisis estadístico de las variables. 
	% [Pedro] sí, estoy de acuerdo. Esto va con el ISSUE #6
\begin{figure}[!h] 
\begin{center}
\begin{tabular}{c}
  \epsfig{file=som43vars.eps,width=11cm} \\
  \epsfig{file=som43umatrix.eps,width=5cm}
\end{tabular}
\caption{\small{Initial data analysis, using 43 descriptive variables per book, %FERGU: la figura está en español, pero ya lo sabréis :P
using SOM.}}
	% Cojollos, ¿qué trabajo os cuesta poner esto en inglés directamente? - JJ
	% [Pedro] sí, si estoy de acuerdo... hay días que me "sale" el texto en inglés,
	% pero hay días que soltar la parrafada en español me resulta más fácil    :/
        % Sería más bien exploratory data analysis o data visualization. 
        % Un gráfico no es un análisis. Y pon las cosas cortas en inglés, hombre - JJ
\label{fig:som43}
\end{center}
\end{figure}

@@

Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{SUBJECT} were included, while %FERGU: vale, no useis SUBJECT, usad mejor SUBJECT (SUBJECT es materia de física, creo xD).    ok, ¡gracias!
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS ON SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.

@@

\begin{minipage}{2.3in} \begin{verbatim}
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
TOTAL DISTRIBUTED
RETAIL PRICE
SUBJECT
EDITORIAL
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

@@

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book can be shown 
in Table \ref{tabla:results7}.
Although in this dataset each book is described using a smaller number of 
variables, two categorical variables, \emph{EDITORIAL} and \emph{SUBJECT}, are 
included, what that makes harder to process the instances and build the different 
models.

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  M5P     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  kNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7} %FERGU: es normal que con menos variables tarde más? Sí, el uso de MATERIA y EDITORIAL hacen que el conjunto sea endiablado.
\end{table*}

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:results13} 
and \ref{tabla:results7}, using those categorical variables as part of a big 
data set makes the problem hard to solve, both in required time to build the 
forecasting models as well as in the obtained errors.
However, as stated before, Trevenque expert sales manager, taking into account 
his knowledge in industry experience and their perceptions, decided that 
\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

Taking into account the SVM model obtained results, this method obtains the lower 
%FERGU: "the best errors" no se sabe si es lo mejor o lo peor xDD Pon "worst results" o así
errors. Even when used using the default parameter values it exhibit a good 
generalization performance.
However, it is much slower than the others to build the model, not only when 
using the data set with 13 input variables, but when using the data set with %FERGU: a veces pones dataset: unificarlo
7 input variables (including \emph{EDITORIAL} and \emph{SUBJECT}).

@@

As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
building (not only parameter and weights setting, but also time to train the 
network) and the fact that it is a back-box model, and thus, it is difficult 
to explain how the forecasts are obtained.
In these experiments, the MLP requires a higher time than other methods, but also
the obtained errors are worse as no parameter tuning to build the models have
been carried out.
Also, the difficulty to process information related to variables \emph{EDITORIAL} 
and \emph{SUBJECT} might affect the worse results obtained on the final dataset.
